Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-02 paper_review/response_20200826.txt

Dear Dr. Endl,

We thank you for organizing the review of our paper, and also
thank the referee for constructive criticism.  We have considered
the referee's remarks carefully and revised our manuscript
accordingly.

Below, we have reproduced the relevant portions of the referee's
report, alongside our responses. A list of changes is appended to
the manuscript using the trackchanges AASTeX macros. Figures
supporting the verification of our SB2 injection-recovery test,
and supporting our radial velocity semi-amplitude/period upper
limits have also been uploaded for inspection.

@@

******************************************
REFEREE COMMENT
----------
Sec. 2.1
Have the authors performed a by-eye search for additional
transits in the light curve?

RESPONSE
----------
> We did perform a by-eye search for additional transits in the
> light curve, and we did not find any compelling events. The
> logical next step -- quantifying our sensitivity through
> injection-recovery simulations -- would be an interesting
> exercise.  For it to be valid, care would need to be taken to
> marginalize out dependence on the detrending method (e.g.,
> David et al 2019 and 2020's experience which led to the
> four-planet V1298 Tau system).  Given the required level of
> effort, we feel this exercise to be outside the scope of the
> present analysis.

******************************************
REFEREE COMMENT
----------
Sec. 2.2
Given that Gaia typically resolves binaries at separations > 1
arcsec, is the blending scenario between Star A and TOI 837
plausible?

RESPONSE
----------
> Referring to the "Gaia" line in the bottom sub-panel of our
> Figure 6 (which came from Rizzuto et al., 2018), at 2.3
> arcseconds of separation between Star A and TOI 837, Gaia
> typically resolves binaries to brightness contrasts of ΔG ~=
> 5.0. The actual brightness difference between the two is 4.7
> G-band magnitudes. So yes, we believe that the blending
> scenario is plausible, primarily because Star A is much fainter
> than TOI 837, placing it near the resolution threshold.

@@

******************************************
REFEREE COMMENT
----------
Sec. 2.2
It seems another line of evidence against Star B (rho=5.4 arcsec)
as the host is the difference imaging centroid test mentioned in
Section 2.1, which they state localizes the transit to within 2
arcseconds of the target.

RESPONSE
----------
> Correct -- we have modified the wording in Sec 2.4 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Given that TOI 837 and Star A have a large contrast but similar
distances, I would expect the two stars to have a large
difference in their expected densities. Can the mean stellar
density from the transit fit be used to further argue that the
planet orbits TOI 837?

RESPONSE
----------
> Our thanks for this point. We have added a paragraph at the end
> of Section 2.4.1 to this effect, though we continue to place
> the strongest weight on our tests from the seeing-limited
> photometric timeseries data.

@@

******************************************
REFEREE COMMENT
----------
Sec. 2.5.1
For the secondary spectral line injection, it is not clear
whether a synthetic spectrum was added to the raw spectrum before
deriving the LSD profile - or whether a synthetic LSD profile was
added to the true profile. It is not clear that the two
procedures would yield the same results.

RESPONSE
----------
> We have updated the manuscript to clarify that the SB2
> grid-search injection and recovery exercise was conducted with
> the secondary signal injected into the LSD profiles, not the
> spectra. 
> 
> To test the validity of this technique, we injected a second
> set of lines to the original spectra, and compared the
> resulting derived LSD profiles. To inject a second set of lines
> to the raw spectrum, we made use of a high SNR CHIRON spectrum
> of a G0 RV standard star, scaled its flux, and blended it with
> the averaged observed spectrum of TOI-837.  We then performed
> the LSD routine on the blended spectrum to derive its LSD
> broadening profile as we would for a normal observation.
> 
> The attached figure shows the resulting LSD profiles from our
> injection test. The left column (black) shows the LSD profiles
> when the secondary signals were injected directly into the LSD
> profile. The right column (red) shows the results of our
> blended spectrum analysis. There is minimal difference between
> the two injection techniques.

******************************************
REFEREE COMMENT
----------
Sec. 3.1.3
The outer separation of the "Not SB2" constraint in the top panel
of Fig. 6 seems optimistic. Wouldn't the velocity separation of a
binary with a=100 AU be less than the broadening of 15 km/s?

RESPONSE
----------
> Correct -- thank you raising for this point. We have amended
> the outer limit in Figure 6 for the "Not SB2" associated
> companion constraint to the distance at which the Keplerian
> orbital velocity falls below the rotational broadening.  The
> text in Sec 3.1.3 has been accordingly.
>
> This weaker constraint now leaves a miniscule region of the HEB
> parameter space open. We do not think that this warrants a
> recalculation of the false positive probability for the system,
> but nonetheless we have added a footnote in the first paragraph
> of Section 3.2 to draw attention to this point.

@@

******************************************
REFEREE COMMENT
----------
Sec. 3.1.4
It is not clear how the range of K-P parameter space stated was
explored in detail. MCMC sampling is inefficient for multimodal
distributions, and given the sparse sampling of the RV time
series, it seems likely that multiple modes exist. Was K fit
independently over a grid of periods? Orbital inclination would
also be an important parameter to include. If models were used to
transform mass ratio limits to contrast limits this should be
explicitly stated.

RESPONSE
----------
> Prompted by this comment, we have amended our method for sampling
> K-P parameter space to one that we feel is more robust against
> inefficient sampling and the multimodal nature of the long-period
> detection problem. The last paragraph of Section 3.1.4 has been
> amended to the following:
>
> """
> To place limits on the properties of a possible bound hierarchical
> companion, we performed the following injection-recovery
> exercise.  We simulated $10^6$ two-body systems with random orbital
> phases and inclinations, and drew their semi-amplitudes and periods
> from logarithmic distributions: $K\ [{\rm m\,s^{-1}}] \sim
> \log\mathcal{U}(1,10^7)$, and $P\ [{\rm days}] \sim \log
> \mathcal{U}(1, 10^{15})$. Again assuming circular orbits, we then
> analytically evaluated what the radial velocities would have been at
> the observed FEROS times if the system had the assumed parameters.
> We then calculated what the linear slope would have been for each
> simulated system.  If the absolute value of the slope exceeded our
> 3-$\sigma$ limit of $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
> day}^{-1}$, we assumed that we would have detected such a system.
> Figure~\ref{fig:fpscenario} shows the resulting limits; weakened
> sensitivity at harmonics of the baseline occur at lower masses and
> smaller projected separations than shown on the plot. The conversion
> from mass to brightness contrast was performed using the same
> isochrone models and assumptions as in Section 3.1.2.}
> """
>
> As a supplement for the referee's inspection, we also attach a plot
> showing the simulated "detections" and "non-detections" directly in
> the Msini vs semi-major axis plane (yellow points are detected;
> purple are not).

@@

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
It is not immediately clear that the mass-temperature-age
combination of ~1.2 Msun, 5960 K, and 30-45 Myr is incorrect. The
mass-temperature relation for stars in this mass range is not the
same on the pre-main sequence as it is on the main sequence.

RESPONSE
----------
> Looking at the MIST isochrones, it seems that a
> solar-metallicity, 1.1Msun star reaches the ZAMS around
> log(age) of 7.5, or ~32 Myr. So, TOI 837 seems likely to be
> roughly at the ZAMS, rather than particularly early in its
> pre-main sequence contraction.
>
> Regardless, we have modified the wording here to reflect that
> our preference for the stellar parameters from "Method 2" is
> linked to our ability to more easily quantify its uncertainties
> (statistical and systematic -- see below).

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
The authors are encouraged to explore the effect of adopting a
different set of evolutionary models. The Dartmouth models of
Feiden (2016), which include a magnetic field prescription, have
been shown to more accurately reproduce the parameters of
pre-main sequence stars. In the mass range of TOI 837 the effects
may not be dramatic, but are likely to be significant compared to
the quoted uncertainty on e.g. the stellar mass. I would expect
that a 10% uncertainty on the stellar mass would be more
realistic (in the sense that it would accommodate systematic
uncertainties) than the currently quoted 1% uncertainty.

RESPONSE
----------
> Thank you for this suggestion, which we agree is important. We
> amended Section 4.2.4 to explore the use of the PARSEC models
> in addition to the MIST models. (We checked the Feiden 2016
> Dartmouth models, but could not find synthetic Gaia-band
> photometry, which would have complicated the comparison between
> between the Gaia photometry and the models.) The differences
> between MIST and PARSEC are now described in the text, and are
> used to estimate systematic uncertainties on the stellar
> parameters.  These uncertainties are now reported in Table 4,
> and they are also propagated through the transit fits (Table 5;
> Figure 1; Figure 4; Figure 10). 
>
> Compared to the initially submitted TESS-only transit fit, the
> wider priors on R* and logg* exacerbated the impact parameter
> vs Rp/R* degeneracy.  With the wider stellar density prior,
> impact parameters much greater than 1 became statistically
> allowed, though not favored, if the planet-to-star radius
> ratio were to be very large. Our ability to break the
> degeneracy was broken! Given only the TESS data + the
> isochronal stellar parameter priors with systematic
> uncertainties included, only a one-sided limit on the planet
> radius can be derived.
>
> One way to "fix" this issue would have been to impose a prior
> constraint that Rp<3Rjup, based on our mass upper limit of
> ~2Mjup and the fact that all known planetary and stellar
> objects follow mass-radius relations that would require the
> planet to be smaller than 3Rjup. However, this approach would
> be somewhat atypical, and even when doing it, we found with our
> updated stellar uncertainties that the TESS-only model (with Rp
> limit prior) gave:
>
>   TESS-only, Rp<3Rjup assumed, systematic star uncertainties:
>     r_planet [Rjup]: 0.836 +0.208 -0.121
>     b: 0.957 +0.027 -0.017
> 
> where we quote median, 86th, and 14th percentiles. Conversely,
> the fit to the combined TESS+ground data yielded a planet
> radius more precise by a factor of ~2x: 
>
>   TESS+ground, broad Rp/R* prior, systematic star uncertainties:
>     r_planet [Rjup]: 0.768 +0.091 -0.072
>     b: 0.936 +0.013 -0.010
>
> Given the increase from 5 to 12 transits, this is presumably
> because the transit depth is measured more precisely. (Both
> sets of chains are fully converged, with Rhat-1 < 1e-4).
> Despite our initial reservations about using the ground-based
> data for the planet parameters, the combined data do yield a
> more precise fit, and also seem to do a better job at breaking
> the Rp/R* vs b degeneracy. These two points persuaded us to
> adopt it as our preferred solution.  Nonetheless, this decision
> is one of preference, and not modelling necessity. We have
> amended Section 4.3 at some length to present the points made
> in this response, and to emphasize the key results from both
> approaches.  Consequent changes include:
>
> * Bottom panel of Figure 1 now shows the TESS+ground data
>   phase-folded, instead of TESS-only. Caption was updated
>   accordingly.
>
> * Figure 10 is now the posterior from TESS+ground, instead of
>   TESS-only.
>
> * Figure 11 was updated for the new planet radius.  
>
> * The planet radius was updated in the abstract and throughout
>   the manuscript.

@@

******************************************
REFEREE COMMENT
----------
Sec. 4.3
The authors perform a joint fit of the TESS and ground-based
photometry to derive a more precise ephemeris, but fit only the
TESS data for the remaining planet parameters. If the errors on
the respective data sets are properly scaled (including jitter
terms if needed), the extra noise from the ground-based
photometry should not significantly impact the inferred
parameters when including those data. This is merely a comment,
and no extra work is necessary.

RESPONSE
----------
> As described above, we have amended our preferred solution to
> the TESS+ground solution, rather than the TESS-only solution.

@@

******************************************
REFEREE COMMENT
----------
Given the planet's young age, it would be interesting to know if
the transit photometry meaningfully constrains the eccentricity
(which along with impact parameter could explain the short
duration). Was a transit fit including eccentricity performed? If
not, there are methods to infer the eccentricity from the
posteriors of a circular orbit fit (see Dawson & Johnson 2012).

RESPONSE
----------
> While we agree that the possibility of a non-circular orbit
> would be interesting, we do not expect that given the present
> data we can make credible statements about potential non-zero
> eccentricities. We have updated the last paragraph of Sec 4.3
> to justify this assumption of a circular orbit, and have
> amended the conclusion to mention this as a possible area for
> future work.

@@

******************************************
REFEREE COMMENT
----------
Discussion
More emphasis could be placed on the unusually large size of the
planet. Some speculative discussion on the nature of this
inflation could be warranted. Figure 11 might also be revised to
also reflect the effect of insolation (or the data plotted could
be restricted to close-in planets).

RESPONSE
----------
> Thank you for this suggestion. We have added a sub-plot in
> Figure 11 showing planet sizes and orbital periods, with the
> sub-100 Myr old planets emphasized.  We considered also
> including a plot with planet insolations on the ordinate
> instead of orbital periods, but the NASA Exoplanet Archive
> column for planet insolation is much less complete, presumably
> owing to the sparsity of available stellar luminosities.  We
> have also added some words in the discussion to the effect that
> that the young planets could be large because of i) a selection
> effect or ii) atmospheric escape.

******************************************
REFEREE COMMENT
----------
The paper ends on a note about nodal precession. Is it simple to
compute the nodal precession timescale given some reasonable
assumptions? This might help determine how likely it is that the
effect may be observed in the near term.

RESPONSE
----------
> Our thanks for this comment, which prompted us to calculate the
> precession frequency of the orbital axis due to the stellar
> oblateness using equations from Anderson+2018 and Lai+2018. We
> found that given the observed parameters of the system and an
> assumed stellar Love number (k2) equal to that of the Sun, the
> precession period would be 45,000 years. To complete say 1% of
> a precession cycle, which might roughly be what is needed to
> observe noticeable changes, we would need to wait ~450 years.
>
> We have correspondingly amended the last sentence to omit the
> point on nodal precession, in favor of the point that more
> photometry should improve our ability to constrain the orbital
> eccentricity, and will also let us search for additional
> transiting planets.

### 2020-09-02 paper/ms.tex
fix tex column width

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
Predicted timescales for photoevaporation and core-powered mass loss
range from 10 million years to over 1 gigayear for typical transiting
sub-Neptunes
\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
The relative importance of each process is set by the planetary
surface gravity and the radiation environment.  Both processes can be
directly observed through observations of planetary winds in the
metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

Beyond physical changes, dynamical changes are expected in the
semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change in step with the viscous evolution of the disk
\citep{lin_orbital_1996}.  High-eccentricity migration processes
including planet-planet scattering, secular chaos, and Kozai-Lidov
oscillations can also occur \citep[{\it
e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
The circularization timescale is thought to be such that for any giant
planets that migrated early, their orbits should circularize within
100 million years \citep{zahn_tidal_1977,bonomo_gaps_2017}.

@@

\explain{NOTE: removed footnote to Damasso et al 2020 in prep, since
it has now been published, and added note to Donati et al 2020.}
A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~\replaced{2523}{2423}, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26,
and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
\added{
The planetary nature of at least two of these signals has been debated
\citep{donati_magnetic_2020,damasso_gaps_2020}.
}

@@

The transits of \pn\ are grazing the stellar limb, which is a cause
for concern.  Particularly for a star near the galactic plane
($b=-5.8^\circ$), background eclipsing binaries are a major source of
astrophysical false positives \citep[{\it
e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
and related scenarios are unlikely to the degree that we can
validate the planet, {\it i.e.}, determine that its probability of
being an astrophysical false positive is small.  We
considered this result worth reporting because of the planet's youth.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.79\textwidth]{f1a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Light curves of \tn.}
    {\it Top}:
    TESS \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    TESS transits.  Gray lines are the best-fit model to the TESS
    \added{and ground-based data}, which includes
    a local quadratic trend for each transit. Gray points are 2-minute
    \texttt{PDCSAP} flux measurements, black points are binned to
    15-minute intervals.  {\it Bottom}: Phase-folded TESS and
    ground-based transits. \added{Section~\ref{subsec:groundphot} presents
    the ground-based data.} Gray points are flux
    measurements with the local spot-induced variation removed.  A
    weighted binning at 6-minute intervals yields the black points.
    The black error-bar shows the median uncertainty for the black
    points.  The gray line is the best-fit model for the entire
    dataset.
		\label{fig:thephot}
	}
\end{figure*}

@@

\added{The top panel of} Figure~\ref{fig:thephot} shows the
\added{TESS} data.  The dominant modulation induced by starspots
coming into and out of view has a peak-to-peak amplitude of about
2.3\%, and a period of about 3 days.  The dips are suggestive of a
grazing transiting planet, recurring roughly every 8 days with a depth
of about 0.4\%.  A few flares are also visible.  A phase-folded view
of the TESS transits \deleted{with starspot variability
removed}\added{combined with ground-based follow-up photometry} is
shown in \added{the bottom panel of }Figure~\ref{fig:thephot}.
\added{The ground-based data }and our procedure for fitting the
models \deleted{in these plots is described in }\added{are discussed
in Sections~\ref{subsec:groundphot} and~\ref{subsec:planet}
respectively}.  \added{First though, some prerequisite context on the
stellar neighborhood of \tn\ is needed.}

@@

\added{
An additional line of evidence for Star A not being the transit host
was also noted by the referee.  The $G$-band magnitude and the
parallax suggest that Star A is an M dwarf. As a probable cluster
member, it would have $Bp - Rp \approx 2.8$ (see
Section~\ref{subsec:hr}), which corresponds roughly to a mass in the
range of 0.15-0.45$\,M_\odot$, or densities roughly in the range of
2-3$\,{\rm g}\,{\rm cm}^{-3}$ based on the PARSEC isochrones
\citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
These densities are inconsistent with those inferred from the transit
fits in Section~\ref{subsec:planet}.
}

@@

To place limits on the properties of a possible bound hierarchical
companion, we \added{performed the following injection-recovery
exercise.  We simulated $10^6$ two-body systems with random orbital
phases and inclinations, and drew their semi-amplitudes and periods from logarithmic
distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
assuming circular orbits, we then analytically evaluated what the
radial velocities would have been at the observed FEROS times if the
system had the assumed parameters.  We then calculated what the linear
slope would have been for each simulated system.  If the absolute
value of the slope exceeded our 3-$\sigma$ limit of $|\dot{\gamma}| <
0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we assumed that we would have
detected such a system.  Figure~\ref{fig:fpscenario} shows the
resulting limits; weakened sensitivity at harmonics of the baseline
occur at lower masses and smaller projected separations than shown on
the plot. The conversion from mass to brightness contrast was
performed using the same isochrone models and assumptions as in
Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
velocity data for a Keplerian orbit assuming wide logarithmic priors
on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.}

@@

The constraints on false-positive scenarios summarized in
Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
are caused by hierarchical blends\added{\footnote{There is
a small gap in the upper panel of
Figure~\ref{fig:fpscenario}, corresponding to a $\approx 0.7 M_\odot$
companion HEB at a projected separation of $\approx$15$\,$AU. This
region of parameter space is, in our view, small enough to be safely
ignored.}}, and {\it iii)} the eclipses are caused by neighboring
stars outside $\approx 2''$.  The only scenario not formally ruled out
is a background eclipsing binary.  A simple, and fallacious, argument 
against background blends follows from counting
statistics.  The local density of $T<15.1$ stars around \tn, found by
counting from TIC8, is $3.7\times10^{-4} \,{\rm arcsec}^{-2}$.
Therefore within the relevant $\approx0.3''$ radius not excluded by
the SOAR HRCam contrast curve, for a randomly selected star we would
expect $1.0\times10^{-4}$ potential $T<15.1$ contaminants, which
appears small.

@@

%\input{starparams.tex}

@@

In ``Method 2'', we \deleted{simply} used the observed location of
\tn\ in the HR diagram and interpolated against the 40$\,$Myr
\added{MIST} isochrone.  This method leverages the relative location
of \tn\ within the \deleted{narrow} \cn\ isochrone to derive precise,
theoretically self-consistent constraints on all of the stellar
parameters.  Although this approach would fail for a low-mass star,
\tn\ is above the stellar masses where the Gaia photometry and
isochrone models begin to diverge.
\added{
  The statistical uncertainties yielded by this approach are of order
  1\% for the stellar mass and radius.  To quantify the systematic
  uncertainties, we compared the parameters derived from the MIST
  isochrones with those from the
  PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}} isochrones
  \citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
  The PARSEC isochrones gave a stellar mass 5\% lower, effective
  temperature 3\% lower, logarithmic surface gravity 1\% lower, and
  radius 8\% lower than the MIST isochrones.  For the sake of
  self-consistency, in Table~\ref{tab:starparams} and the ensuing
  analysis we adopted the stellar
  parameter values from MIST.  We took the uncertainties to be the
  quadrature sum of the statistical and systematic components.
}

@@

%\input{model_posterior_table.tex}

>>>>

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
Predicted timescales for photoevaporation and core-powered mass loss
range from 10 million years to over 1 gigayear for typical transiting
sub-Neptunes
\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
The relative importance of each process is set by the planetary
surface gravity and the radiation environment.  Both processes can be
directly observed \replaced{through observations of planetary winds
in}{in favorable cases using} the metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

Beyond physical changes, dynamical changes are expected in the
semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change in step with the viscous evolution of the disk
\citep{lin_orbital_1996}.  High-eccentricity migration processes
including planet-planet scattering, secular chaos, and Kozai-Lidov
oscillations can also occur \citep[{\it
e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
The circularization timescale is thought to be such that for any giant
planets that \replaced{migrated early}{do migrate early}, their orbits
should circularize within 100 million years
\citep{zahn_tidal_1977,bonomo_gaps_2017}.

@@

\explain{NOTE: removed footnote to Damasso et al 2020 in prep, since
it has now been published, and added note to Donati et al 2020.}
\replaced{A}{To date, a} few dozen planets in clusters have been
detected, and fewer still have been closely characterized.  Despite
the challenges of starspot-induced radial velocity (RV) variations, RV
surveys found early success in the Hyades, NGC~\replaced{2523}{2423},
Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26,
and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
\added{The planetary nature of at least two of these signals has been
debated \citep{donati_magnetic_2020,damasso_gaps_2020}.}

@@

The transits of \pn\ are grazing the stellar limb, which is a cause
for concern.  Particularly for a star near the galactic plane
($b=-5.8^\circ$), background eclipsing binaries are a major source of
astrophysical false positives \citep[{\it
e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data showed that
this and related scenarios were unlikely to the degree that we could
validate the planet, {\it i.e.}, determine that its probability of
being an astrophysical false positive was small.  We considered this
result worth reporting because of the planet's youth.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f1a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.76\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Light curves of \tn.}
    {\it Top}:
    TESS \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    TESS transits.  Gray lines are the best-fit model to the TESS
    \added{and ground-based data}, which includes a local quadratic
    trend for each transit. Gray points are 2-minute \texttt{PDCSAP}
    flux measurements, black points are binned to 15-minute intervals.
    {\it Bottom}: Phase-folded TESS and ground-based transits.
    \added{Section~\ref{subsec:groundphot} presents the ground-based
    data.} Gray points are flux measurements with the local
    spot-induced variation removed.  A weighted binning at 6-minute
    intervals yields the black points.  The black error-bar shows the
    median uncertainty for the black points.  The gray line is the
    best-fit model for the entire dataset.
		\label{fig:thephot}
	}
\end{figure*}

@@

\added{The top panel of} Figure~\ref{fig:thephot} shows the
\added{TESS} data.  The dominant modulation induced by starspots
coming into and out of view has a peak-to-peak amplitude of about
2.3\%, and a period of about 3 days.  The dips are suggestive of a
grazing transiting planet, recurring roughly every 8 days with a depth
of about 0.4\%.  A few flares are also visible.  A phase-folded view
of the TESS transits \deleted{with starspot variability
removed}\added{combined with ground-based follow-up photometry} is
shown in \added{the bottom panel of }Figure~\ref{fig:thephot}.
\added{The ground-based data }and our fitting procedure \deleted{in
these plots is described in }\added{are discussed in
Sections~\ref{subsec:groundphot} and~\ref{subsec:planet}
respectively}. \added{First though, some prerequisite context on the
stellar neighborhood of \tn\ is needed.}

@@

\added{An additional line of evidence for Star A not being the
transit host was also noted by the referee.  The $G$-band magnitude
and the parallax suggest that Star A is an M dwarf. As a probable
cluster member, it would have $Bp - Rp \approx 2.8$ (see
Section~\ref{subsec:hr}), which corresponds roughly to a mass in the
range of 0.15--0.45$\,M_\odot$, or densities roughly in the range of
2--3$\,{\rm g}\,{\rm cm}^{-3}$ based on the PARSEC isochrones
\citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
These densities are inconsistent with those inferred from the transit
fits in Section~\ref{subsec:planet}.}

@@

To place limits on the properties of a possible bound hierarchical
companion, we \added{performed the following injection-recovery
exercise.  We simulated $10^6$ two-body systems with random orbital
phases and inclinations, and drew their semi-amplitudes and periods
from logarithmic distributions: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^7)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(1, 10^{15})$. Again assuming circular orbits, we then
analytically evaluated what the radial velocities would have been at
the observed FEROS times if the system had the assumed parameters.  We
then calculated what the linear slope would have been for each
simulated system.  If the absolute value of the slope exceeded our
3-$\sigma$ limit of $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
day}^{-1}$, we assumed that we would have detected such a system.
Figure~\ref{fig:fpscenario} shows the resulting limits; weakened
sensitivity at harmonics of the baseline occur at lower masses and
smaller projected separations than shown on the plot. The
interpolation from mass to brightness contrast was performed using the
same isochrone models and assumptions as in
Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
velocity data for a Keplerian orbit assuming wide logarithmic priors
on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting 3-$\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.}

@@

The constraints on false-positive scenarios summarized in
Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
are caused by hierarchical blends\added{\footnote{There is a small gap
in the upper panel of Figure~\ref{fig:fpscenario}, corresponding to a
$\approx 0.7 M_\odot$ companion HEB at a projected separation of
$\approx$15$\,$AU. This region of parameter space is small, and we
ignore it in the remaining analysis.}}, and {\it iii)} the eclipses
are caused by neighboring stars outside $\approx 2''$.  The only
scenario not formally ruled out is a background eclipsing binary.  A
simple, and fallacious, argument against background blends follows
from counting statistics.  The local density of $T<15.1$ stars around
\tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
not excluded by the SOAR HRCam contrast curve, for a randomly selected
star we would expect $1.0\times10^{-4}$ potential $T<15.1$
contaminants, which appears small.

@@

@@

In ``Method 2'', we \deleted{simply} used the observed location of
\tn\ in the HR diagram and interpolated against the 40$\,$Myr
\added{MIST} isochrone.  This method leverages the relative location
of \tn\ within the \deleted{narrow} \cn\ isochrone to derive precise,
theoretically self-consistent constraints on all of the stellar
parameters.  Although this approach would fail for a low-mass star,
\tn\ is above the stellar masses where the Gaia photometry and
isochrone models begin to diverge. \added{The statistical
uncertainties yielded by this approach are of order 1\% for the
stellar mass and radius.  To quantify the systematic uncertainties, we
compared the parameters derived from the MIST isochrones with those
from the PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}}
isochrones
\citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
The PARSEC isochrones gave a stellar mass 5\% lower, effective
temperature 3\% lower, logarithmic surface gravity 1\% lower, and
radius 8\% lower than the MIST isochrones.  For the sake of
self-consistency, in Table~\ref{tab:starparams} and the ensuing
analysis we adopted the stellar parameter values from MIST.  We took
the uncertainties to be the quadrature sum of the statistical and
systematic components.}

@@
